CTL mapping - The added value from segregating correlation

### 2012-01-30 inst/methodPaper/document.tex
No idealized cut-off, use the permutations

  \begin{figure*}[ht]
    \begin{center}
    \vspace{-0.2cm}
    \hspace{-1.3cm}
    \subfigure[CTL profiles]{
      \includegraphics[keepaspectratio,scale=.26]{img/ctl_qtl.pdf}
      \label{subfiga}
    }
    \hspace{0.3cm}
    \subfigure[Traits x Traits interaction matrix]{
      \includegraphics[keepaspectratio,scale=.65]{img/ctl_pxp.pdf}
      \label{subfigb}
    }
    \hspace{0.3cm}
    \subfigure[Reconstructed network]{
      \includegraphics[keepaspectratio,scale=.17]{img/ctl_net.pdf}
      \label{subfigc}
    }
  \end{center}
  \begin{minipage}{7in}
  \label{newplots}
  \vspace{-0.7cm}
  \caption[Plots]{
  {\emph {\bf a}}: Example CTL + QTL profiles (red). Seen are the QTL profile on top of the CTL profile. 
  The first peak is a CTL caused by X4.Methylsulfinylbutyl and X5.Methylthiopenty showing a significant 
  difference in correlation, we don't observe a QTL for this location. 
  {\emph {\bf b}}: Traits x Traits interaction matrix (TxT matrix). Information obtained using CTL mapping, 
  showing for each trait the significance of the difference in correlation to all other traits. This 
  matrix can be transformed into .sif file to generate a network image. 
  {\emph {\bf c}}:  Reconstructed network, this shows the same information as the TxT matrix only in a more accessible way, we visualized our 
  network using cytoscape, the linewidth is the summarized interaction evidence.
 }
\end{minipage}
\vspace{-0.5cm}
\end{figure*}

>>>>

  \begin{figure*}[ht]
    \begin{center}
    \vspace{-0.2cm}
    \hspace{-1.3cm}
    \subfigure[CTL profiles]{
      \includegraphics[keepaspectratio,scale=.3]{img/ctl_qtl.pdf}
      \label{subfiga}
    }
    \hspace{0.3cm}
    \subfigure[Traits x Traits interaction matrix]{
      \includegraphics[keepaspectratio,scale=.3]{img/ctl_pxp.pdf}
      \label{subfigb}
    }
    \hspace{0.3cm}
    \subfigure[Reconstructed network]{
      \includegraphics[keepaspectratio,scale=.2]{img/ctl_net.pdf}
      \label{subfigc}
    }
  \end{center}
  \begin{minipage}{7in}
  \label{newplots}
  \vspace{-0.7cm}
  \caption[Plots]{
  {\emph {\bf a}}: Example CTL + QTL profiles (red). Seen are the QTL profile on top of the CTL profile. 
  The first peak is a CTL caused by X4.Methylsulfinylbutyl and X5.Methylthiopenty showing a significant 
  difference in correlation, we don't observe a QTL for this location. 
  {\emph {\bf b}}: Traits x Traits interaction matrix (TxT matrix). Information obtained using CTL mapping, 
  showing for each trait the significance of the difference in correlation to all other traits. This 
  matrix can be transformed into .sif file to generate a network image. 
  {\emph {\bf c}}:  Reconstructed network, this shows the same information as the TxT matrix only in a more accessible way, we visualized our 
  network using cytoscape, the linewidth is the summarized interaction evidence.
 }
\end{minipage}
\vspace{-0.5cm}
\end{figure*}
